---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# qsort

## Overview

qsort is package that allows scoring Q-sort data,
using criteria sorts and derived scales from subsets of items.
The qsort package includes descriptions and scoring procedures
for four different Q-sets:  
Attachment Q-set (version 3.0) (Waters, 1995);  
California Child Q-set (Block & Block, 1969);  
Maternal Behaviour Q-set (version 3.1) (Pederson et al., 1999);  
Preschool Q-set (Baumrind, 1968 revised by Wanda Bronson).  

qsort package includes 3 objects:  
* `qsort_score()` a function for scoring Q-sort data;  
* `qsets` a list with four data frames used in qsort_score(),
containing criterion scores and scales for the referred Q-sets;  
* `ex_qsort` a list containing four example data frames for the referred Q-sets.  

Access `qsets` help file (`?qsets`) to learn more about
which criteria sorts and scales included for each Q-set.

## Installation

The qsort package can be installed from GitHub:  

```{r, eval = F}
# to install packages from github you first need to install devtools package from CRAN.
# if you haven't done so already just type
# install.packages("devtools")
devtools::install_github("joaordaniel/qsort")
```

## Example

The example bellow shows how to use `qsort_score()` function
to compute scores from California Child Q-sort data,
present in `ex_qsort` datasets (`ex_qsort$ccq`).  

```{r example}
library(qsort)
data_ccq <- qsort_score(ex_qsort$ccq, qset = "ccq", item1 = "ccq1", subj_id = "participant", group_id = "classroom")
data_ccq
```

Access `qsort_score` help file (`?qsort_score`)
to learn more about the function's four arguments,
and `qsets` help file (`?qsets`) to learn more about variables' names.  

## References
Baumrind, D. (1968). Manual for the Preschool Behaviour Q-set.
Parental Research Project. Berkeley, CA: Institute of Human Development.  
Block, J. H., & Block, J. (1969). The California Child Q-Set. Berkeley, CA:
Institute of Human Development, University of California.  
Pederson, D. R., Moran, G., & and Bento, S. (1999). Maternal Behaviour
Q-sort (version 3.1). London, ON: Psychology Department, Western University.  
Waters, E. (1995). Appendix A: The attachment Q-set (Version 3. 0).
Monographs of the Society for Research in Child Development, 60, 234-246.  
