---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(qsort)
```

# qsort

The qsort package allows the computation of social competence and
self-esteem scores for California Child Q-set (CCQ; Block and Block, 1969)
and Preschool Q-set data (PQ; Baumrind, 1968 revised by Wanda Bronson),
as described in Waters et al. (1985). The package includes a dataset
with all CCQ and PQ Q-set items and the corresponding criterion scores
for social competence, self-esteem and social desirability.

The qsort package can be installed from github:

```{r, eval = F}
# to install packages from github you first need to install devtools package,
# if you haven't done so already
# install.packages("devtools")
devtools::install_github("joaordaniel/qsort")
```

## Example

The example bellow shows how to use qsort_score function
to compute CCQ social competence and self-esteem scores
from data present in ex_qsort dataset

```{r example}
data_ccq <- qsort_score(ex_qsort, qset = "ccq", subj_id = "participant", group_id = "classroom")
data_ccq
```
