---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/qsort)](https://cran.r-project.org/package=qsort) [![Rdoc](http://www.rdocumentation.org/badges/version/qsort)](http://www.rdocumentation.org/packages/qsort) 
[![Build Status](https://travis-ci.org/joaordaniel/qsort.svg?branch=master)](https://travis-ci.org/joaordaniel/qsort)
[![DOI](https://zenodo.org/badge/132877059.svg)](https://zenodo.org/badge/latestdoi/132877059)

# qsort

## Overview

`qsort` is a package that allows scoring Q-sort data,
using criteria sorts and derived scales from subsets of items.
This package includes descriptions and scoring procedures
for four different Q-sets:

* Attachment Q-set (version 3.0) (Waters, 1995);
* California Child Q-set (Block & Block, 1969);      
* Maternal Behaviour Q-set (version 3.1) (Pederson et al., 1999);
* Preschool Q-set (Baumrind, 1968 revised by Wanda Bronson).  

qsort package includes 7 objects:

* `qsort_score()` a function for scoring Q-sort data;
* `qset_aqs` a data frame containing the Attachment Q-set (aqs; version 3.0);
* `qset_ccq` a data frame containing the California Child Q-set (ccq);
* `qset_mbqs` a data frame containing the Maternal Behaviour Q-set (mbqs; version 3.1);
* `qset_pq` a data frame containing the Preschool Q-set (pq);
* `ex_qsort` a list containing four example data frames for the referred Q-sets;
* `print_cards()` a function for printing Q-set item cards.

Read the documentation (with `?qset_aqs`, `?qset_ccq`, `?qset_mbqs` and `?qset_pq`) to learn more about
which criteria sorts and scales are included for each Q-set.

## Installation

The `qsort` package can be installed from GitHub:  

```{r, eval = F}
# to install packages from github you first need to install devtools package from CRAN.
# if you haven't installed devtools already just type:
install.packages("devtools")

# to install qsort from github type:
devtools::install_github("joaordaniel/qsort")
```

To install `qsort` package from CRAN:
```{r, eval = F}
install.packages("qsort")
```

## Example

The example bellow shows how to use `qsort_score()` function
to compute scores from California Child Q-sort data,
present in `ex_qsort` datasets (`ex_qsort$ccq`).  

```{r, eval = TRUE, echo = TRUE}
library(qsort)
data_ccq <- qsort_score(ex_qsort$ccq, qset_ccq, item1 = "ccq1", subj_id = "participant", group_id = "classroom", qsort_length = 100)
data_ccq
```

Read `qsort_score` help file (`?qsort_score`)
to learn more about the function's four arguments,
and `qset_ccq` help file (`?qset_ccq`) to learn more about variables' names.


## Print cards

To print item descriptions in separate cards use `print_cards()` function.
The example bellow uses the `print_cards()` function to create a pdf file
in a user defined directory (e.g., "C:/Users/jd/R/") with Attachment Q-set items.

```{r, eval = FALSE, echo = TRUE}
library(qsort)
print_cards(qset_aqs, desc_col = "description", dir.print = "C:/Users/jd/R/")
```
Read `print_cards()` help file (`?print_cards`)
to learn more about the function's two arguments.

## Contributing

[Contribution guidelines for this project](.github/CONTRIBUTING.md)

## References
Baumrind, D. (1968). Manual for the Preschool Behaviour Q-set.
Parental Research Project. Berkeley, CA: Institute of Human Development.    

Block, J. H., & Block, J. (1969). The California Child Q-Set. Berkeley, CA:
Institute of Human Development, University of California.      

Pederson, D. R., Moran, G., & Bento, S. (1999). Maternal Behaviour
Q-sort (version 3.1). London, ON: Psychology Department, Western University. 

Waters, E. (1995). Appendix A: The attachment Q-set (Version 3.0).
Monographs of the Society for Research in Child Development, 60, 234-246.     
